SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-26 quiz.tex
More question templates.

\begin{table}[t]
\caption{Quiz question templates.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Definition}		&Ask for the class that fits the given textbook definition.\\
Example					&What is defined as \enquote{Examination of in and out patients in radiological department}?\\
Distractors				&Labels of other classes (that have a path of length 2 or less to the correct class.)\\
\midrule
\textbf{Subject}		&Ask for the class that is related via a given relation to a given object.\\
						&Key: Who is \emph{involved in} a \emph{healthcare network}?\\
Example					&Stem: \\
Distractors				&Labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object, for example .\\
\midrule
\textbf{Intertwined}	&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\midrule
\textbf{CloseMatch}		&\\
						&Stem: In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Example:				&Key: Chief Information Officer – Department of Information management – IM Staff \\
						&Distractors: Labels of three resources connected in one of the distractor shapes in \cref{fig:intertwined}, such as
						Chief Information Officer – Strategic Gap – Corporate Strategy\\
\midrule
\textbf{}				&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\bottomrule
\end{tabulary}
\end{table}

@@

\paragraph{contains}
describe contains...

@@

\begin{table}
\begin{tabulary}{\textwidth}{LLLL}
\toprule
Question			&Correct answer	&Distractor 1	&Distractor 2\\ 
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? &Chief Information Officer -- Department of Information management -- IM Staff & Chief Information Officer -- Strategic Gap -- Corporate Strategy & Chief Information Officer -- Ticket Evaluation -- Project Monitoring \\
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? & IM -- IT Service Management -- Operational IM & IM -- Tactical Management of Information Systems -- Information System & IM -- methodology of IM -- Operational Management of Information Systems\\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Jour Fixe Execution -- Project Monitoring & Chief Information Officer -- Project Risk -- Strategic HIS Planning & Chief Information Officer -- IT General Ledger Account Planning -- Project Portfolio \\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Project Presentation -- Project Waitlist & Chief Information Officer -- Strategic IM Planning -- Project Manager & Chief Information Officer -- Project Priorisation -- Project Web Site \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{intertwined}-questions and answers.}
\label{tab:intertwined}
\end{table}

Intertwined focuses on the connectivity of the knowledge graph.
In each answer, three related concepts are given.
The correct answer is the one where all concepts are directly connected with each other, that is, they form a triangle in the graph, see \cref{fig:intertwined}.
The distractors should then not form this triangle.
In the difficult variation of the distractor, one of the three concept pairs is directly connected, one has a shortest path of length 2 and the third one has neither.
In this easier variation, two concepts pairs are connected with a shortest path of length 2 instead.
Examplse are given in \cref{tab:intertwined}.

>>>>

\begin{table}[t]
\caption{Quiz question templates.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Definition}		&Ask for the class that fits the given textbook definition.\\
						&Stem: \emph{What is defined as \enquote{Examination of in and out patients in radiological department}?}\\
Example:				&Key: label of the class with that definition, e.g. \emph{CT Scanner}\\
						&Distractors: Labels of other classes, that have a path of length 2 or less to the correct class., e.g. \emph{Execution of Diagnostic and Therapeutic Procedures}, \emph{Imaging Modality}\\
\midrule
\textbf{Subject}		&Ask for the class that is related via a given relation to a given object.\\
						&Stem: Who is \emph{involved in} a \emph{healthcare network}?\\
Example					&Key: \\
						&Distractors: Labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object, for example .\\
\midrule
\textbf{Intertwined}	&\\
						&Stem: In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Example:				&Key: Chief Information Officer – Department of Information management – IM Staff \\
						&Distractors: Labels of three resources connected in one of the distractor shapes in \cref{fig:intertwined}, such as
						Chief Information Officer – Strategic Gap – Corporate Strategy\\
\midrule
\textbf{CloseMatch}		&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\midrule
\textbf{Contains}		&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\midrule
\textbf{Label-Definition}	&Present different definitions and ask, which of them fits the given entity.\\
						&Stem: \emph{How is \enquote{X} defined?}, e.g. \emph{Chief Executive Officer}\\
Example:				&Key: definition of the entity, e.g. \emph{Responsible for setting and carrying out the strategic plans and policies of an enterprise.}\\
						&Distractors: labels of entities within a path length of at most 2, e.g. \emph{Anyone who has direct or indirect influence on or interest in a component of an information system.}\\
\midrule
\textbf{}				&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\bottomrule
\end{tabulary}
\end{table}

@@

\paragraph{subject}
describe subject (contains)...

@@

\iffalse
\begin{table}
\begin{tabulary}{\textwidth}{LLLL}
\toprule
Question			&Correct answer	&Distractor 1	&Distractor 2\\ 
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? &Chief Information Officer -- Department of Information management -- IM Staff & Chief Information Officer -- Strategic Gap -- Corporate Strategy & Chief Information Officer -- Ticket Evaluation -- Project Monitoring \\
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? & IM -- IT Service Management -- Operational IM & IM -- Tactical Management of Information Systems -- Information System & IM -- methodology of IM -- Operational Management of Information Systems\\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Jour Fixe Execution -- Project Monitoring & Chief Information Officer -- Project Risk -- Strategic HIS Planning & Chief Information Officer -- IT General Ledger Account Planning -- Project Portfolio \\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Project Presentation -- Project Waitlist & Chief Information Officer -- Strategic IM Planning -- Project Manager & Chief Information Officer -- Project Priorisation -- Project Web Site \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{intertwined}-questions and answers.}
\label{tab:intertwined}
\end{table}
\fi

Intertwined focuses on the connectivity of the knowledge graph.
In each answer, three related concepts are given.
The correct answer is the one where all concepts are directly connected with each other, that is, they form a triangle in the graph, see \cref{fig:intertwined}.
The distractors should then not form this triangle.
In the difficult variation of the distractor, one of the three concept pairs is directly connected, one has a shortest path of length 2 and the third one has neither.
In this easier variation, two concepts pairs are connected with a shortest path of length 2 instead.
%Examplse are given in \cref{tab:intertwined}.
